基于Lab色彩空间的太阳黑子手绘图背景提取方法

### 2017-01-15 paper/paper.tex
修改关键词
微调英文摘要

\textbf{关键词: }图像分割；太阳黑子；Lab色彩空间；K-means聚类

\textbf{Abstract: }Sunspots drawings is a traditional way of recording sunspots activities. Digitization of the drawings help the long-term storage of the data and the research of it. Background extraction is an important step in the process of digitization. For this problem, we developed a rapid background extraction method based on Lab color space. In this method, we perform two-class K-means cluster for the $a$, $b$ component of Lab color space on the drawings. The cluster result shows that the background and handdrawing part are clustered into two class accurately. For mass drawings background extraction, we only select a part of drawings perform the aformentioned cluster, then apply their result on other drawings. Experiment result shows that this method enormously speed up the time of processing and guaranteed the accuracy at the same time.

\textbf{Keywords: }image segmentation；sunspot；CIELAB color space；k-means clustering

>>>>

\textbf{关键词: }背景提取；太阳黑子；Lab色彩空间；K-means聚类

\textbf{Abstract: }Sunspots drawings is a traditional way of recording sunspots activities. Digitization of the drawings is beneficial to long-term storage and research of the data. Background extraction is an important step in the process of digitization. For this problem, we develope a rapid background extraction method based on Lab color space. In this method, we perform two-class K-means cluster for the $a$, $b$ component of Lab color space on the drawings. The cluster results show that the background and the handdrawing part are clustered into two class accurately. For mass drawings background extraction, we only select a part of drawings to perform the aformentioned cluster, then apply their result on other drawings directly. The experimental results show that this method not only enormously speed up the time of processing, but also guaranteed the accuracy.

\textbf{Keywords: }background extraction；sunspot；CIELAB color space；k-means clustering
